\TheTitle

### 2017-07-12 paper/study.tex
Study: Adding commit selection

% \textbf{User Opinion and Profile}

% Finally, we ask the user for their opinions on the tools and for some
% information about their level of experience with git.  \dmg{be more
%   precise: understanding or preference is too broad. What you want to
%   know answers to specific questions regarding how the tools compare and
%   which ones they would prefer} The first three questions are intended
% to provide us with a better understanding of preference, and insight on
% why, the participant had that preference.  The last three questions in
% this section are aimed at getting a better understanding of the
% demographic of our participants.
% \begin{enumerate}
%   \item Given these tasks again, which tool would you prefer to use?
%   \item Which aspects of each tool did you like and why?
%   \item How long have you used git?
%   \item If you have used git, for what kind of projects? (personal,
%     school courses, professional?)
%   \item If you have used git, how many commits, files, and contributors
%     were involved with the largest repository you have worked with?
% \end{enumerate}

@@

@@

\dmg{see my comments in previous section. it is ok to explain them here,
  but you need to explain what they are briefly in the previous section}

We chose two commits for use in the study. The order that the commits
are presented is randomized between participants, but the order is kept
consistent through the tasks described in the next subsection.

\dmg{this place does not require a description of the database. This
  requires just to say the commits/merge set (dates and numbers are ok)
  only} We use the \tool database, containing commits and merge-tree
information from April 16th 2005 to October 14th, 2014, which
corresponds to being between Linux release 2.6.12-rc3 and Linux
3.17-rc1. \evan{Cite the database even more?} \dmg{again, i have
  problems with your writing: ``we wanted to use in the study commits of
  different size, to determine if the size had an impact in the
  completion of the tasks. We chose commits of three different sizes...}
We chose the commits based on tree sizes. We \dmg{we didn't find: this
  is a fact, not a discovery; what is a majority? 50\%+1? be precise}
\dmg{drop the word inner, and do it in order: 25\% of trees have only
  one commit, 50\%.., 75\%...} found that a majority of the trees
contain at most seven inner commits, while more than 25\% of the trees
contain a single commit. 75\% of the tree contained up to 51 inner
commits and merges, and finally the largest tree contained 7217 nodes.
We chose to work with the trees in \dmg{if you are going to use the
  words quartile, just use them before in your description eg: the
  distribution of the sizes of the trees is x, y merges, whose size
  corresponded to the 25 ,50 quartiles, simple and precisee} the first
and second quartile, as merge trees of sizes between one and seven, not
including the merge into the master branch, make up the majority of the
trees in the database.

\dmg{remove from here, what is here? this is not a road trip :)} From
here, we selected one tree from the trees of a single commit at random.
Selecting a commit from that tree is trivial, as there is only one to
choose.\dmg{remove the obvious, instead concentrate on why the others
  are not trivial}

We selected one tree of size seven at random from all trees of size
seven\dmg{how many where there?}. We placed a restriction the trees, the
selected tree must include at least one internal merge to increase the
complexity of the trees tested. For each randomly selecting a tree, we
chose one of its internal commits at random (using the
\verb|random.choice| function in python 3.6.1).

\dmg{question: so you chose only one commit of each size, and the
  randomization was which tool to use for each question? or did they
  have to do the same task for two commits?}

Using this technique, we selected commit
\emph{a3c1239eb59c0a907f8be5587d42e950f44543f8} from the tree containing
a single node (Figure~\ref{fig:commit_1}), which we will refer to as
\comA, and commit \emph{cdbdd1676a5379f1d5cbd4d476f5e349f445befe}, from
the tree containing seven nodes (Figure~\ref{fig:commit_2}), which we
will refer to as \comB.

>>>>

We include two commits in the study to detect differences between merge
tree sizes. The order that the commits are presented to each participant
is randomized. We analyzed the 15096 merge-trees from April 16th 2005 to
October 14th 2014, which corresponds to the releases Linux 2.6.12-rc3
and Linux 3.17-rc1. 25\% of the trees contain at most a single commit
not including the root, while 50\% of the trees contain at most seven
nodes non-root nodes.
% TODO: get the number for this if there is time
75\% of the trees contain at least 51 nodes, and the largest tree
contains 7217 nodes.

From this information, we selected one tree with a single commit, and
one tree with seven other nodes to represent a small tree and a
medium-sized tree. A majority of the trees are flat, where all nodes
merge directly into the root node. Of the 8031 trees containing at least
seven nodes, only 593 contained at least a single internal merge node.
Trivially, trees with a single node cannot have any internal nodes, and
of the 624 trees with seven nodes, only 135 contained at least one inner
node. To increase the complexity of the medium-sized tree, we randomly
selected one of the 135 trees to represent the medium tree.

From the 2008 trees containing only a single node, we selected one at
random, and trivially selected the only commit in the tree. From the
trees containing seven nodes, we selected one randomly, then randomly
selected one of the commits in the tree. We selected commit
\emph{a3c1239eb59c0a907f8be5587d42e950f44543f8} from the tree containing
a single node, which we will refer to as \comA, and commit
\emph{cdbdd1676a5379f1d5cbd4d476f5e349f445befe} from the tree containing
seven nodes, which we will refer to as \comB. A visual representation
for these trees is shown in Figure~\ref{fig:study_commits}.

@@

The study begins with a short introduction to the \mt model, followed by
an introduction to Gitk and \tool. We provided two examples of
converting the DAG to the \mt. The first DAG was a flat merge, so the
corresponding merge tree did not have any internal nodes. The second was
not a flat merge, so the corresponding merge tree contained a single
internal node. Any questions about the model were answered at this time.
Following the introduction to the \mt model, we introduce Gitk and
\tool, providing information about what each pane shows in Gitk, and
what each tab does in \tool.

To mitigate the bias between tools, commits, and tasks, we randomize the
orders.

@@
